Well-quasi-orderings on word languages

### 2024-10-17 src/prelims.tex
Format

\paragraph*{Finite words.} In this paper, we use letters $\Sigma, \Gamma$ to
denote finite alphabets, $\Sigma^*$ to denote the set of finite words over
$\Sigma$, and $\varepsilon$ for the empty word in $\Sigma^*$. In order to give
some intuition on the decision problems, we will sometimes use the notion of
finite automata, regular languages, and Monadic Second Order ($\intro*\MSO$)
logic on finite words, and assume is familiar with them. We refer to the
textbook of \cite{THOM97} for a detailed introduction to this topic.

@@

Let $(X, \leq)$ be a \kl{well-quasi-ordered} set. One can define three
well-founded trees from $X$: the tree of \kl{bad sequences}, the tree of
decreasing sequences, and the tree of \kl{antichains}. The rank of these
respective trees are called respectively the \kl{maximal order type}
\cite{dejongh77}, the \kl{ordinal height} \cite{schmidt81}, and the \kl{ordinal
width} of $X$ \cite{kriz90b}. We refer to the survey of \cite{DZSCSC20} for a
detail discussion on these concepts and their computation on specific classes
of well-quasi-ordered sets.

>>>>

\paragraph*{Finite words.} In this paper, we use letters $\Sigma, \Gamma$ to
denote finite alphabets, $\Sigma^*$ to denote the set of finite words over
$\Sigma$, and $\varepsilon$ for the empty word in $\Sigma^*$. In order to give
some intuition on the decision problems, we will sometimes use the notion of
\intro{finite automata}, \intro{regular languages}, and \intro{Monadic Second
Order} ($\intro*\MSO$) logic on finite words, and assume is familiar with them.
We refer to the textbook of \cite{THOM97} for a detailed introduction to this
topic.

@@

Let $(X, \leq)$ be a \kl{well-quasi-ordered} set. One can define three
well-founded trees from $X$: the tree of \kl{bad sequences}, the tree of
decreasing sequences, and the tree of \kl{antichains}. The rank of these
respective trees are called respectively the \intro{maximal order type} of $X$
written $\intro*{\oType{X}}$ \cite{dejongh77}, the \intro{ordinal height} of
$X$ written $\intro*{\oHeight{X}}$ \cite{schmidt81}, and the \intro{ordinal
width} of $X$ written $\intro*{\oWidth{X}}$ \cite{kriz90b}. We refer to the
survey of \cite{DZSCSC20} for a detail discussion on these concepts and their
computation on specific classes of well-quasi-ordered sets.
